A Massive Molecular Gas Reservoir in the $z$\,=\,2.221 Type-2 Quasar Host Galaxy SMM\,J0939+8315 lensed by the Radio Galaxy 3C220.3

### 2015-07-19 skeleton.tex
Need to finish discussion and appendix

\begin{abstract}
We report the detection of \CO line emission in the strongly-lensed submillimeter galaxy\,(SMG) SMM\,J0939+8315 at $z$\,=\,2.2212\,$\pm$\,0.0001, using  
the Combined Array for Research in Millimeter-wave Astronomy (CARMA). 
The SMG is lensed by the radio galaxy 3C220.3 and its companion galaxy at $z$\,=\,0.685. 
This measurement allows us to place constraints on the intrinsic properties
of the cold gas and dust in the interstellar medium (ISM) of the background SMG which hosts a type-2 quasar, as well as on the spectral energy distribution (SED) of the foreground radio galaxy using the marginally resolved continuum 
emission detected at an integrated flux density of $S_\nu$\,=\,7.5\,$\pm$\,1.3 mJy
 at 104 GHz.
We measure a velocity-integrated \CO line intensity of $I_{\rm CO(3-2)}$\,=\,(10.7\,$\pm$\,1.3)\,Jy\,km\,s\pmOne,
corresponding to a lensing- and excitation-corrected CO line luminosity of \Lp\,=\,(2.9\,$\pm$\,0.8)\,$\times$\,10$^{10}$\,(10.1/$\mu_{\rm L}$)\,\LpU, where $\mu_{\rm L}$ is the lensing magnification factor inferred from our lens modeling of the 1\,mm continuum emission. 
 This
translates to a molecular gas mass of $M_{\rm gas}$\,=\,(2.3\,$\pm$\,0.6)\,$\times$\,10$^{10}$\,\Msun. We 
fit optically thick and optically thin modified blackbody models to the SED of the SMG. The preferred optically thick model yields a characteristic dust temperature of $T_{\rm dust}$\,=\,63.1$^{+1.1}_{-1.3}$\,K in the rest-frame, a dust mass of $M_{\rm dust}$\,=\,(5.2\,$\pm$\,2.1)\,$\times$\,10$^8$\,\Msun, and a total infrared (IR) luminosity of $L_{\rm IR}$\,=\,(9.1\,$\pm$\,1.2)\,$\times$10$^{12}$\,\Lsun, after correcting for lensing magnification. We conclude that the intrinsics properties (\eg gas mass, gas mass 
fraction, star formation rate) of the molecular gas reservoir in SMM
J0939+8315 based on our \CO observations is similar to other high redshift
SMGs. 
\end{abstract}
\keywords{galaxies: formation --- galaxies: high-redshift --- submillimeter: galaxies}

@@

\section{Observations}\label{sec:obs}
\subsection{CARMA} \label{sec:carmadata}
Observations of the \CO rotational transition ($\nu_{\rm rest}$\,=\,345.7959899 GHz) toward the background galaxy SMM
J0939 ($z$\,=\,2.221) were carried out using CARMA at a redshifted frequency of $\nu_{obs}$\,=\,107.357\,\,GHz (2.79\,\,mm)  (program ID: cf0142; P.I.: Riechers). The 3\,mm receivers were used to cover the redshifted \CO line and the nearby 2.88\,mm continuum emission, employing a correlator setup providing a bandwidth of 3.75 GHz in each sideband and a spectral resolution of 5.208 MHz ($\sim$14.5 km\,\,s\pmOne). The line was placed in the
upper sideband, with the local oscillator tuned to $\nu_{\rm LO}$\,$\sim$104.2609 GHz.
Observations were carried out under good
weather conditions in the E array configuration on 2014 July 12. This resulted in 1.56 hours of 15 antenna-equivalent on-source time after discarding unusable visibility data.
The nearby source J1039+811 (0.65\,\,Jy) was observed every 20 minutes for
pointing, amplitude, and phase calibration. Mars was observed as the primary
absolute flux calibrator, and the quasar 3C273 was observed as the secondary
flux calibrator. J0927+390 was observed for bandpass calibration, yielding $\sim
$15\% calibration accuracy.
The {\sc MIRIAD} package was used to calibrate and analyze the visibility data, which are deconvolved and imaged using
the CLEAN algorithm with ``natural" weighting. This yields a synthesized clean beam size of 11$\farcs$3\,$\times$\,6\farcs1, at a position angle of $-$56.1$\degr$ east of north for the upper sideband image cube. 
The rms noise of the data prior to continuum subtraction is $\sigma_{\rm ch}$\,=\,8.75\,\,mJy\,\,beam\pmOne\ per bin 
with a channel width of $\sim$29 km\,\,s\pmOne
% spectra
, whereas the final rms noise of the continuum subtracted data is $\sigma_{\rm ch}$\,=\,8.71\,\,mJy\,\,beam\pmOne\ per bin with 
the same channel width, and $\sigma$\,=\,1.00\,Jy\,\,km\,\,s\pmOne\,\,$\rm beam^{-1}$ over a channel 
width of 198 MHz (corresponding to $\sim$553\,\,km\,\,s\pmOne). 
%mom0
The continuum image is created by
averaging over all line-free channels, this yields a synthesized clean beam size of 11\farcs9\,$\times$\,6\farcs5, at a position angle of $-$55.9$\degr$ east of north and an 
rms noise of 0.51\,\,mJy\,\,beam\pmOne.

\section{Results}\label{sec:res}
%\subsection{New Results: Continuum Emission} 
\subsection{New Results: 3C220.3} 
Averaging over all line-free channels, we detect continuum emission at 9$\sigma$ significance at an averaged frequency of $\nu_{cont}$\,=\,104.2106 GHz ($\sim$2.9 mm) in the observed-frame, corresponding to 175.6 GHz ($\sim$1.7 mm) at $z$\,=\,0.685. In this lens system, the 
foreground galaxy (3C220.3) is radio-loud, we thus expect the continuum emission to be dominated by the foreground galaxy (see \S \ref{sec:SEDFg} for details). We use CASA's {\sc imfit} task to estimate the peak position of the continuum emission. The deconvolved source size is (10\farcs9\,$\pm$\,4\farcs0)\,$\times$\,(3\farcs4\,$\pm$\,2\farcs1), and the integrated flux density is 7.50\,$\pm$\,1.30\,\,mJy. At the peak position of the continuum emission, the peak flux density is S$_\nu$\,=\,4.91\,$\pm$\,0.54\,\,mJy\,\,beam\pmOne. An overlay image of the 104 GHz continuum emission on the 9 GHz continuum measurement (H14) is shown in Figure \ref{fig:cont}. This demonstrates that at the resolution of our observations, the continuum emission is marginally resolved. It is therefore plausible that non-thermal emission from both the lobes and the radio core dominate the integrated flux density in our measurement.

The frequency range of our observations covers the HCO$^+$(2$-$1), HNC($J$\,=\,2\,$\rightarrow$\,1), and H$_2$O(3$_{13}$\,$-$\,2$_{20}$) 
transition line emission in the foreground galaxy, at 
the redshifted frequencies of 105.86, 107.71, and 108.79\,\,GHz, respectively. We establish 3$\sigma$ upper limits employing a typical line width of 
$\sim$\,300\,\,km\,\,s\pmOne, based on the CO($J$\,=\,1\,$\rightarrow$\,0) line measurement in the sample of local radio galaxies \citep[$z$ $<$ 0.1; ][]{Smolcic11a}, resulting in 3$\sigma$ of 7.839\,\,Jy\,\,km\,\,s\pmOne.\\ \\
Question for DR: 3sigma using FWHM or total line width (FWZI?)

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.80\textwidth]{Figure/ContPanel.pdf}
\caption{Left: Contour map of the 104 GHz continuum emission in 3C220.3. The beam size is 11\farcs9\,$\times$\,6\farcs5, at P.A.\,=\,
$-$56$\degr$, as indicated in the bottom left corner. Right: Contours of the CARMA 104 GHz continuum emission (red) from the 
foreground radio galaxy 3C220.3 overlaid on the 9 GHz emission (green contours and grayscale; H14). The synthesized beam size of the VLA observations is 0$\farcs$6\,$\times$\,0$\farcs$2, at P.A. 
76$\degr$. The central cross on each image indicates the position of the radio core of 3C220.3. The contour levels of the 104 GHz continuum emission start at $\pm$3$\sigma$, incrementing at steps 
of $\pm$1$\sigma$ of 0.5 mJy beam\pmOne; the contour levels of the 9 GHz continuum 
emission start at $\pm$4$\sigma$ where $\sigma$\,=\,0.064 mJy beam\pmOne\ and increment at steps of $\pm$2$^n\sigma$, 
where $n$ is a positive integer.
\label{fig:cont}}
\end{figure*}
%\subsection{New Results: \CO Line Emission}
\subsection{New Results: SMM\,J0939\\ \CO Line Emission}
We detect \CO line emission at $\sim$10(?yes?no?)$\sigma$ significance toward the background SMG SMM\,J0939 at $z$\,=\,2.221.
The spatial extent of this SMG is $\sim$5$\arcsec$, as shown in the Submillimeter Array (SMA) 1\,mm dust continuum in Figure \ref{fig:mom0}; as such, the detected \CO line emission is spatially unresolved. 
The line profile in Figure \ref{fig:mom0} is therefore extracted at the peak position of the unresolved CO emission. Fitting a four-parameter single Gaussian to the spectrum yields a peak flux density of 21.83\,$\pm$\,2.68\,\,mJy, superimposed on a continuum level of 4.19\,$\pm$\,0.49\,\,mJy, and full width at half-maximum (FWHM) of 557\,$\pm$\,36\,\,km\,\,s\pmOne. 
We construct a velocity-integrated (0th moment) map of the \CO 
emission from the data after subtracting continuum emission in the visibility plane. This results in a velocity-integrated \CO line flux of $S_{\rm CO}$\,=\,10.7\,$\pm$\,1.3 Jy km\,\,s\pmOne\ over the FWZI velocity range of $\Delta v\sim$\,914 km\,\,s\pmOne, the uncertainty does not include $\sim$\,15\% calibration uncertainty. We ignore primary beam correction given that the source is close to the phase center and is unresolved (\ie much smaller than the primary beam size). Our \CO line measurement confirms the redshift of SMM\,J0939, yielding $z$\,=\,2.22122\,$\pm$\,0.00007.

@@

\subsection{SED Fitting} \label{sec:SED}
\subsubsection{3C220.3}\label{sec:SEDFg}
Synchrotron continuum emission from extended components of a radio galaxy decreases with increasing radio frequencies, 
and the spectrum is commonly characterized by a power law distribution $S \propto \nu^{-\alpha}$, where the 
spectral index $\alpha$ is $\gtrsim$ 0.5. While the contribution from extended components decreases, studies using 
samples of radio galaxies have suggested that the flat/inverted-spectrum of the compact radio core component rises 
and dominates the flux density at higher frequencies \citep{Kellermann81a,Begelman84a}. This has been observed in a FR-II galaxy at a similar redshift\,--\,3C220.1 at the redshift of $z$\,=\,0.610, where observations were carried out at observed-frame $\sim$\,90 GHz \citep{Hardcastle08a}. It is noteworthy that prior to our observations, 3C220.1 was the only FR-II galaxy with high frequency observations at $z$\,$>$\,0.6. Previous studies of the core component of 3C220.3 have established upper 
limit of $<$ 0.17 mJy at 4.6 GHz \citep{Mullin06a} and an unambiguous detection of 0.8 mJy at 9 GHz (H14), suggesting a substantially inverted spectrum of the core (Figure \ref{fig:SED}).
Consequently, we may naively expect the integrated flux density in our continuum detection of $S_{\rm 104GHz}$\,=\,7.50\,$\pm$\,1.30\,\,mJy to be dominated by the unresolved core component of the foreground FR-II galaxy, which is at $z$\,=\,0.685. 
However, the inferred deconvolved spatial size of the source matching that in the resolved image (see Figure 1) is 
suggestive of a marginally resolved detection of the extended components with non-negligible emission. 
This is plausible given that the orientation of the synthesized beam in our observations is in alignment with the 
axis along the 
lobes of the radio galaxy, as shown in Figure \ref{fig:cont}. We investigate this disparity by fitting models to 
existing SED data of the total integrated flux as listed in Table \ref{tab:SEDdataRadio}, and extrapolating the fit to 
estimate the flux density of the lobes at the frequency of our continuum measurement. 
\input{table_SED}
Following Equation (1) in \citet{Cleary07a}, the fit to the lobe emission can be expressed as a parabolic function:
\begin{equation}
\log F_{\nu}^{\mathrm lobe} (\nu) \propto - \beta\ (\log\ \nu - \log \nu_{t})^2  + \log (\exp({\frac{\nu}{\nu_c^{\mathrm lobe}}}))
\end{equation}
where $F_{\nu}^{\mathrm lobe}$ is the flux density of the lobes, $\beta$ is a parameter representing the bending 
of the parabola, $\nu_t$ is the frequency at which the optical depth of the synchrotron emitting plasma reaches 
unity, and $\nu_c^{\rm lobe}$ is the frequency corresponding to the cutoff energy of the lobe plasma energy 
distribution. 
The extrapolated flux density at 104\,\,GHz is consistent with the flux density of our continuum 
measurement (Figure \ref{fig:SED}). The 9$\sigma$ detection of the continuum thereby suggests
a dominant contribution from the lobes, and the peak flux density therefore does not appear to be emission toward 
the core. Moreover, the peak position of the 104\,\,GHz continuum is
centered toward the northern lobe (Figure \ref{fig:cont}), which further supports our argument. We did not 
extrapolate the core measurements to the frequency of our continuum, as previous measurements of the core are 
taken 
across different epochs. 
EDIT HERE \par
From our interpretation, we place an upper limit of $S_\nu$\,$<$\,2.59 mJy on the core component using the difference.
\par
Studies by \citet{Meisenheimer89a} and \citet{Hardcastle08a} have suggested spectra of hotspots are flat up to optical frequencies, where some exhibit spectral steepening in cm and mm wavelengths (\eg 3C123). At the resolution of our observations, it is unclear whether the integrated flux is dominated by the emission from the compact hotspot or the emission from the surrounding diffuse lobe components.

\begin{figure}[!tbph]
\centering
\includegraphics[width=0.5\textwidth]{Figure/3C220_3_FullSED_longticks.pdf}
\caption{The SED of 3C220.3 (solid purple line) and SMM\,J0939 (dashed purple line and solid cyan line) including the new measurements presented in this paper. 
Black dots represent existing data of 3C220.3 (see Table \ref{tab:SEDdataRadio}). Red dots at 104 GHz correspond to 
our continuum measurements (integrated, peak, and difference). The purple line corresponds to the parabolic function we 
fit to the data associated with the radio galaxy, following \citet{Cleary07a}. The dashed purple line and 
the solid cyan line correspond to the best-fit SED models of the background SMG. The photometric data of the SMG are reported by H14. \label{fig:SED}}
\end{figure}

\subsubsection{SMM\,J0939+8315} \label{sec:SEDBg}
To constrain the dust and gas properties in the ISM of SMM\,J0939, we perform SED fitting to the
photometric data obtained with {\it Herschel}/PACS and SPIRE, at wavelengths
between observed-frame 70 \micron $-$ 500 \micron, and interferometric data with the SMA at 1\,mm (H14). We use the publicly
available software {\sc mbb\_emcee}\footnote{https://github.com/aconley/mbb\_emcee} to perform the SED fitting; the code uses an affine-invariant Markov chain Monte
Carlo (MCMC) approach, and further details of the code are given by \citet{Riechers13a} and \citet{Dowell14a}. The
functional form of the fit comprises a single-temperature, modified blackbody function joined to a $S_{\lambda} \propto \lambda^\alpha
$ power law on the blue
side of the SED.
We fit both optically thick and optically thin models. In the optically thick case, the wavelength $
\lambda_0$\,=\,${c}/{\nu_0}$ is an additional parameter representing the rest-frame wavelength at which the optical
depth $\tau_{\nu} =$ ($\nu$/$\nu_0$)$^\beta$ reaches unity. Thus, the functional form of the modified blackbody
in the optically thick regime is as follows:
\begin{equation}
\rm S_{\lambda} \propto \frac{(1-exp^{-(\frac{\lambda_0 (1+z)}{\lambda})^{\beta}})(\frac{c}{\lambda})^3}
{exp^{\frac{hc}{\lambda\rm{kT/(1+z)} } }-1}
\end{equation}
and in the optically thin regime, the functional form reduces to:
\begin{equation}
\rm S_{\lambda} \propto \frac{(\frac{c}{\lambda})^{\beta+3}}{exp^{\frac{hc}{\lambda\rm{kT/(1+z)}}}-1}
\end{equation}
where $T$ is the rest-frame characteristic cold dust temperature, $\beta$ is the dust emissivity (or spectral index of the dust extinction
curve), and $\alpha$ is the power law spectral index. The overall fit is normalized using the observed-frame 500
$\micron$ flux density, hence this becomes an additional parameter in the fit. For both models, we impose an upper limit on the observed-frame dust temperature ($T/(1+z)$) to 60 K, and for the optically thick model, we impose an upper limit on $\lambda_0$ to 2000\,\,\micron. Additionally, we fix the upper limits on 
$\beta$ to be 3.0 and 2.2 for the optically thin model and optically thick model, respectively.

>>>>

\begin{abstract}
We report the detection of \CO line emission in the strongly-lensed submillimeter galaxy\,(SMG) SMM\,J0939+8315 at $z$\,=\,2.2212\,$\pm$\,0.0001, using  
the Combined Array for Research in Millimeter-wave Astronomy (CARMA). 
The SMG is lensed by the radio galaxy 3C220.3 and its companion galaxy at $z$\,=\,0.685. 
This measurement allows us to place constraints on the intrinsic properties
of the cold gas and dust in the interstellar medium (ISM) of the background SMG which hosts a type-2 quasar, as well as on the spectral energy distribution (SED) of the foreground radio galaxy using the marginally resolved continuum 
emission detected at an integrated flux density of $S_\nu$\,=\,9.5\,$\pm$\,0.6 mJy
 at 104 GHz.
We measure a velocity-integrated \CO line intensity of $I_{\rm CO(3-2)}$\,=\,(10.7\,$\pm$\,1.3)\,Jy\,km\,s\pmOne,
corresponding to a lensing- and excitation-corrected CO line luminosity of \Lp\,=\,(2.9\,$\pm$\,0.6)\,$\times$\,10$^{10}$\,(10.1/$\mu_{\rm L}$)\,\LpU, where $\mu_{\rm L}$ is the lensing magnification factor inferred from our lens modeling of the 1\,mm continuum emission. 
 This
translates to a molecular gas mass of $M_{\rm gas}$\,=\,(2.3\,$\pm$\,0.5)\,$\times$\,10$^{10}$\,\Msun. We 
fit optically thick and optically thin modified blackbody models to the SED of the SMG. The preferred optically thick model yields a characteristic dust temperature of $T_{\rm dust}$\,=\,63.1$^{+1.1}_{-1.3}$\,K in the rest-frame, a dust mass of $M_{\rm dust}$\,=\,(5.2\,$\pm$\,2.1)\,$\times$\,10$^8$\,\Msun, and a total infrared (IR) luminosity of $L_{\rm IR}$\,=\,(9.1\,$\pm$\,1.2)\,$\times$10$^{12}$\,\Lsun, after correcting for lensing magnification. We conclude that the intrinsics properties (\eg gas mass, gas mass 
fraction, star formation rate) of the molecular gas reservoir in SMM
J0939+8315 based on our \CO observations is similar to other high redshift
SMGs. 
\end{abstract}
\keywords{galaxies: formation --- galaxies: high-redshift --- submillimeter: galaxies}

@@

\section{Observations}\label{sec:obs}
\subsection{CARMA} \label{sec:carmadata}
Observations of the \CO rotational transition ($\nu_{\rm rest}$\,=\,345.7959899 GHz) toward the background galaxy SMM
J0939 ($z$\,=\,2.221) were carried out using CARMA at a redshifted frequency of $\nu_{obs}$\,=\,107.357\,\,GHz (2.79\,\,mm)  (program ID: cf0142; P.I.: Riechers). The 3\,mm receivers were used to cover the redshifted \CO line and the nearby 2.88\,mm continuum emission, employing a correlator setup providing a bandwidth of 3.75 GHz in each sideband and a spectral resolution of 5.208 MHz ($\sim$14.5 km\,\,s\pmOne). The line was placed in the
upper sideband, with the local oscillator tuned to $\nu_{\rm LO}$\,$\sim$104.2609 GHz.
Observations were carried out under good
weather conditions in the E array configuration on 2014 July 12. This resulted in 1.56 hours of 15 antenna-equivalent on-source time after discarding unusable visibility data.
The nearby source J1039+811 (0.65\,\,Jy) was observed every 20 minutes for
pointing, amplitude, and phase calibration. Mars was observed as the primary
absolute flux calibrator, and the quasar 3C273 was observed as the secondary
flux calibrator. J0927+390 was observed for bandpass calibration, yielding $\sim
$15\% calibration accuracy.
The {\sc MIRIAD} package was used to calibrate and analyze the visibility data, which are deconvolved and imaged using
the CLEAN algorithm with ``natural" weighting. This yields a synthesized clean beam size of 11$\farcs$3\,$\times$\,6\farcs1, at a position angle of $-$56.1$\degr$ east of north for the upper sideband image cube. 
The rms noise of the data prior to continuum subtraction is $\sigma_{\rm ch}$\,=\,8.75\,\,mJy\,\,beam\pmOne\ per bin 
with a channel width of $\sim$29 km\,\,s\pmOne
% spectra
, whereas the final rms noise of the continuum subtracted data is $\sigma_{\rm ch}$\,=\,8.71\,\,mJy\,\,beam\pmOne\ per bin with 
the same channel width, and $\sigma$\,=\,1.00\,Jy\,\,km\,\,s\pmOne\,\,$\rm beam^{-1}$ over a channel 
width of 198 MHz (corresponding to $\sim$553\,\,km\,\,s\pmOne). 
%mom0
The continuum image is created by
averaging over all line-free channels, this yields a synthesized clean beam size of 11\farcs9\,$\times$\,6\farcs5, at a position angle of $-$55.9$\degr$ east of north and an 
rms noise of 0.49\,\,mJy\,\,beam\pmOne.

\section{Results}\label{sec:res}
%\subsection{New Results: Continuum Emission} 
\subsection{New Results: 3C220.3} 
Averaging over all line-free channels, we detect continuum emission at 9$\sigma$ significance at an averaged frequency of $\nu_{cont}$\,=\,104.2106 GHz ($\sim$2.9 mm) in the observed-frame, corresponding to 175.6 GHz ($\sim$1.7 mm) at $z$\,=\,0.685. In this lens system, the 
foreground galaxy (3C220.3) is radio-loud, we thus expect the continuum emission to be dominated by the foreground galaxy (see \S \ref{sec:SEDFg} for details). We use CASA's {\sc imfit} task to estimate the peak position of the continuum emission. The deconvolved source size is (10\farcs2\,$\pm$\,1\farcs4)\,$\times$\,(6\farcs1\,$\pm$\,0\farcs7), and the integrated flux density is 9.46\,$\pm$\,0.64\,\,mJy. At the peak position of the continuum emission, the peak flux density is S$_\nu$\,=\,5.18\,$\pm$\,0.24\,\,mJy\,\,beam\pmOne. An overlay image of the 104 GHz continuum emission on the 9 GHz continuum measurement (H14) is shown in Figure \ref{fig:cont}. This demonstrates that at the resolution of our observations, the continuum emission is marginally resolved. It is therefore plausible that non-thermal emission from both the lobes and the radio core dominate the integrated flux density in our measurement.

The frequency range of our observations covers the HCO$^+$(2$-$1), HNC($J$\,=\,2\,$\rightarrow$\,1), and H$_2$O(3$_{13}$\,$-$\,2$_{20}$) 
transition line emission in the foreground galaxy, at 
the redshifted frequencies of 105.86, 107.71, and 108.79\,\,GHz, respectively. We establish 3$\sigma$ upper limits employing a typical line width of 
$\sim$\,300\,\,km\,\,s\pmOne, based on the CO($J$\,=\,1\,$\rightarrow$\,0) line measurements in the sample of local radio galaxies \citep[$z$ $<$ 0.1; ][]{Smolcic11a}, resulting in 3$\sigma$ of 7.84\,\,Jy\,\,km\,\,s\pmOne.\\ \\
Question for DR: 3sigma using FWHM or total line width (FWZI?)

\begin{figure*}[tbph]
\centering
\includegraphics[width=0.80\textwidth]{Figure/ContPanel.pdf}
\caption{Left: Contour map of the 104 GHz continuum emission in 3C220.3. The beam size is 11\farcs9\,$\times$\,6\farcs5, at P.A.\,=\,
$-$56$\degr$, as indicated in the bottom left corner. Right: Contours of the CARMA 104 GHz continuum emission (red) from the 
foreground radio galaxy 3C220.3 overlaid on the 9 GHz emission (green contours and grayscale; H14). The synthesized beam size of the VLA observations is 0$\farcs$6\,$\times$\,0$\farcs$2, at P.A. 
76$\degr$. The central cross on each image indicates the position of the radio core of 3C220.3. The contour levels of the 104 GHz continuum emission start at $\pm$3$\sigma$, incrementing at steps 
of $\pm$1$\sigma$ of 0.5 mJy beam\pmOne; the contour levels of the 9 GHz continuum 
emission start at $\pm$4$\sigma$ where $\sigma$\,=\,0.064 mJy beam\pmOne\ and increment at steps of $\pm$2$^n\sigma$, 
where $n$ is a positive integer.
\label{fig:cont}}
\end{figure*}
%\subsection{New Results: \CO Line Emission}
\subsection{New Results: SMM\,J0939\\ \CO Line Emission}
We detect \CO line emission at $\sim$10(?yes?no?)$\sigma$ significance toward the background SMG SMM\,J0939 at $z$\,=\,2.221.
The spatial extent of this SMG is $\sim$5$\arcsec$, as shown in the Submillimeter Array (SMA) 1\,mm dust continuum in Figure \ref{fig:mom0}; as such, the detected \CO line emission is spatially unresolved. 
The line profile in Figure \ref{fig:mom0} is therefore extracted at the peak position of the unresolved CO emission. Fitting a four-parameter single Gaussian to the spectrum yields a peak flux density of 21.83\,$\pm$\,2.68\,\,mJy, superimposed on a continuum level of 4.19\,$\pm$\,0.49\,\,mJy, and full width at half-maximum (FWHM) of 557\,$\pm$\,36\,\,km\,\,s\pmOne. 
We construct a velocity-integrated (0th moment) map of the \CO line 
emission from the data after subtracting continuum emission in the visibility plane. This results in a velocity-integrated \CO line flux of $S_{\rm CO}$\,=\,10.7\,$\pm$\,1.3 Jy km\,\,s\pmOne\ over the FWZI velocity range of $\Delta v\sim$\,914 km\,\,s\pmOne, the uncertainty does not include $\sim$\,15\% calibration uncertainty. We ignore primary beam correction given that the source is close to the phase center and is unresolved (\ie much smaller than the primary beam size). Our \CO line measurement confirms the redshift of SMM\,J0939, yielding $z$\,=\,2.22122\,$\pm$\,0.00007.

@@

\subsection{SED Fitting} \label{sec:SED}
\subsubsection{3C220.3}\label{sec:SEDFg}
Synchrotron continuum emission from extended components of a radio galaxy decreases with increasing radio frequencies, 
and the spectrum is commonly characterized by a power law distribution $S \propto \nu^{-\alpha}$, where the 
spectral index $\alpha$ is $\gtrsim$ 0.5. While the contribution from extended components decreases, studies using 
samples of radio galaxies have suggested that the flat/inverted-spectrum of the compact radio core component rises 
and dominates the flux density at higher frequencies \citep{Kellermann81a,Begelman84a}. This has been observed in a FR-II galaxy at a similar redshift\,--\,3C220.1 at the redshift of $z$\,=\,0.610, where observations were carried out at observed-frame $\sim$\,90 GHz \citep{Hardcastle08a}. It is noteworthy that prior to our observations, 3C220.1 was the only FR-II galaxy with high frequency radio observations at $z$\,$>$\,0.6. Previous studies of the core component of 3C220.3 have established upper 
limit of $<$ 0.17 mJy at 4.6 GHz \citep{Mullin06a} and an unambiguous detection of 0.8 mJy at 9 GHz (H14), suggesting a substantially inverted spectrum of the core (Figure \ref{fig:SED}).
Consequently, we may naively expect the integrated flux density in our continuum detection of $S_{\rm 104GHz}$\,=\,9.46\,$\pm$\,0.64\,\,mJy to be dominated by the unresolved core component of the foreground FR-II galaxy, which is at $z$\,=\,0.685. 
However, the deconvolved spatial size of the source matching that in the resolved image (see Figure 1) is 
suggestive of a marginally resolved detection of the extended components with non-negligible emission. 
This is plausible given that the orientation of the synthesized beam in our observations is in alignment with the 
axis along the 
lobes of the radio galaxy, as shown in Figure \ref{fig:cont}. We investigate this disparity by fitting models to 
existing SED data of the total integrated flux as listed in Table \ref{tab:SEDdataRadio}, and extrapolating the fit to 
estimate the flux density of the lobes at the frequency of our continuum measurement. 
\input{table_SED}
Following Equation (1) in \citet{Cleary07a}, the fit to the lobe emission can be expressed as a parabolic function:
\begin{equation}
\log F_{\nu}^{\mathrm lobe} (\nu) \propto - \beta\ (\log\ \nu - \log \nu_{t})^2  + \log (\exp({\frac{\nu}{\nu_c^{\mathrm lobe}}}))
\end{equation}
where $F_{\nu}^{\mathrm lobe}$ is the flux density of the lobes, $\beta$ is a parameter representing the bending 
of the parabola, $\nu_t$ is the frequency at which the optical depth of the synchrotron emitting plasma reaches 
unity, and $\nu_c^{\rm lobe}$ is the frequency corresponding to the cutoff energy of the lobe plasma energy 
distribution. 
The extrapolated flux density at 104\,\,GHz is consistent with the peak flux density of our continuum 
measurement (Figure \ref{fig:SED}). The 9$\sigma$ detection of the continuum thereby suggests
a dominant contribution from the lobes, and the peak flux density does not appear to be emission toward 
the core. Moreover, the peak position of the 104\,\,GHz continuum is
centered toward the northern lobe (Figure \ref{fig:cont}), which further supports our argument. We did not 
extrapolate the core measurements to the frequency of our continuum, as previous measurements of the core are 
taken 
across different epochs. 
We place an upper limit of $S_\nu$\,$<$\,4.28 mJy on the core component using the difference in flux density.
\par
Studies by \citet{Meisenheimer89a} and \citet{Hardcastle08a} have suggested spectra of hotspots are flat up to optical frequencies, where some exhibit spectral steepening in cm and mm wavelengths (\eg 3C123). At the resolution of our observations, it is unclear whether the flux density is dominated by the emission from the compact hotspot or the emission from the surrounding diffuse lobe components.

\begin{figure}[!tbph]
\centering
\includegraphics[width=0.5\textwidth]{Figure/3C220_3_FullSED2_longticks.pdf}
\caption{The SED of 3C220.3 (solid purple line) and SMM\,J0939 (dashed purple line and solid cyan line) including the new measurements presented in this paper. 
Black dots represent existing data of 3C220.3 (see Table \ref{tab:SEDdataRadio}). Red dots at 104 GHz correspond to 
our continuum measurements (integrated, peak, and difference). The purple line corresponds to the parabolic function we 
fit to the data associated with the radio galaxy, following \citet{Cleary07a}. The dashed purple line and 
the solid cyan line correspond to the best-fit SED models of the background SMG. The photometric data of the SMG are reported by H14. \label{fig:SED}}
\end{figure}

\subsubsection{SMM\,J0939+8315} \label{sec:SEDBg}
To constrain the dust and gas properties in the ISM of SMM\,J0939, we perform SED fitting to the
photometric data obtained with {\it Herschel}/PACS and SPIRE, at wavelengths
between observed-frame 70 \micron\,$-$\,500 \micron, and the interferometric data obtained with the SMA at 1\,mm (H14). We use the publicly
available software {\sc mbb\_emcee}\footnote{https://github.com/aconley/mbb\_emcee} to perform the SED fitting; the code uses an affine-invariant Markov chain Monte
Carlo (MCMC) approach, further details of the code are given by \citet{Riechers13a} and \citet{Dowell14a}. The
functional form of the fit comprises a single-temperature, modified blackbody function joined to a $S_{\lambda} \propto \lambda^\alpha
$ power law on the blue
side of the SED.
We fit both optically thick and optically thin models. In the optically thick case, the wavelength $
\lambda_0$\,=\,${c}/{\nu_0}$ is an additional parameter representing the rest-frame wavelength at which the optical
depth $\tau_{\nu} =$ ($\nu$/$\nu_0$)$^\beta$ reaches unity. Thus, the functional form of the modified blackbody
in the optically thick regime is as follows:
\begin{equation}
\rm S_{\lambda} \propto \frac{(1-exp^{-(\frac{\lambda_0 (1+z)}{\lambda})^{\beta}})(\frac{c}{\lambda})^3}
{exp^{\frac{hc}{\lambda\rm{kT/(1+z)} } }-1}
\end{equation}
and in the optically thin regime, the functional form reduces to:
\begin{equation}
\rm S_{\lambda} \propto \frac{(\frac{c}{\lambda})^{\beta+3}}{exp^{\frac{hc}{\lambda\rm{kT/(1+z)}}}-1}
\end{equation}
where $T$ is the rest-frame characteristic cold dust temperature, $\beta$ is the dust emissivity (or spectral index of the dust extinction
curve), and $\alpha$ is the power law spectral index. The overall fit is normalized using the observed-frame 500
$\micron$ flux density, hence this becomes an additional parameter in the fit. For both models, we impose an upper limit on the observed-frame dust temperature ($T/(1+z)$) to 60 K, and for the optically thick model, we impose an upper limit on $\lambda_0$ to 2000\,\,\micron. Additionally, we fix the upper limits on 
$\beta$ to be 3.0 and 2.2 for the optically thin model and optically thick model, respectively.

\input{table_mbb}
The best-fit values in both regimes are listed in Table \ref{tab:mbb}, and the correlation plots are available in the Appendix. The best-fit solution of an optically thin
model corresponds to $\chi^2$\,=\,5.31 with 3 degrees of freedom, whereas that of an optically thick model
corresponds to $\chi^2$\,=\,2.25 with 2 degrees of freedom, suggesting a better fit than in the optically thin
case. In the subsequent analysis, we employ the inferred values from the optically thick model.
The best-fit solution yields a rest-frame FIR luminosity of $L_{\rm FIR (42.5-122.5\micron)}$\,=\,53.3$^{+1.1}_{-1.1}$\,$\times$\,10$^{12}$\,\Lsun, and a total infrared (IR) luminosity of $L_{\rm IR (8-1000 \micron)}$\,=\,88.5$^{+2.6}_{-2.6}$\,$\times$\,10$
^{12}$\,\Lsun. Assuming a dust absorption coefficient of $\kappa_{\nu}$\,=\,2.64 m$^2$ kg\pmOne\ at 125.0 $
\micron$ \citep{Dunne03a}, we derive the dust mass using the following expression:
\begin{equation}
M_{\rm dust}\,=\,S_{\nu} D_{L}^2 [(1 + z) \kappa_{\nu} B_{\nu}]^{-1} \tau_{\nu} [1-
\exp(-\tau_{\nu})]^{-1}
\end{equation}
where $S_{\nu}$ is the flux density in ergs/s/cm$^{2}$/Hz , $D_{\rm L}$ is the luminosity distance in cm, $\kappa_{\nu}$ is the dust
absorption coefficient in cm$^2$ g\pmOne, $\tau_{\nu}$ is the optical depth, and $B_{\nu}$ is the Planck function,
all quantities are expressed in the observed-frame. We find a dust mass of $M_{\rm dust}$\,=\,50.5$^{20.4}_{-20.2}\times$10$^8$\,\,\Msun, the uncertainties do not include those of $\kappa_{\nu}$. These values are based on SED fitting to the photometric data, \ie prior
to lensing correction.

With the limited amount of data in the FIR waveband, the dust mass is weakly constrained. 
We perform an additional fit using an optically thick model where we loosen the upper limit of $\beta$ from 2.2 to 3.0, while the difference between all best-fit parameters in this scenario and those using an upper limit of 2.2 (see Table \ref{tab:mbb}) is within 3\%, we find that the dust mass is boosted by a factor of $\sim$2.
